\sysfull

### 2017-08-11 paper/evaluation.tex
fixed some red text

We also used an alternative setup where the MSP-TS430RGZ48C launchpad was used for continuous power experiments. We used internal timer for measuring run time\todo{how about EDB?}{Kiwan}. For harvested energy, we used the ThingMagic Astra-EX RFID reader set at 30\,dBm transmission power\todo{say what antenna are you using with what gain}{Kiwan}. Applications were cross-compiled using GCC and Clang, so that we can use LLVM for \sys compiler. Version 3.8.0 was used for both Clang and LLVM.

>>>>

We also used an alternative setup where the MSP-TS430RGZ48C launchpad was used for continuous power experiments. We used internal timer for measuring run time. For harvested energy, we used the ThingMagic Astra-EX RFID antenna set at 30\,dBm transmission power. We used EDB~\cite{edb} to measure run time. Applications were cross-compiled using GCC and Clang, so that we can use LLVM for \sys compiler. Version 3.8.0 was used for both Clang and LLVM.
